Multisequence algorithm for coarse-grained biomolecular simulations: exploring the sequence-structure relationship of proteins

### 2017-06-07 Supplement.tex
Supplement minor change

\section{Supplementary Material}

\begin{figure}
\includegraphics[width=14cm]{meanE}
\caption{ Correlation of average energy as calculated by ST and MS algorithms for our 4 model sequences (A) A1, (B) N1, (C) R1, and (D) R2. Figure shows that  ST and MS are consistent in their calculations. The errors associated with both algorithms are very small such that they are not visible on the scale of the average energy.}
\end{figure}

>>>>

\documentclass[12]{article}

\usepackage[left=3cm, right=2.5cm, top=2.5cm, bottom=3cm]{geometry}
%\usepackage{graphicx}% Include figure files
\usepackage[export]{adjustbox}

\begin{document}

\section*{\LARGE{\textbf{Supplementary Material}}}

\begin{figure}[h]
\includegraphics[width=0.8\textwidth,center]{meanE}
\caption{ Comparison of the average energy, $\left < E\right >$, as calculated at 8 different temperatures by the ST and MS algorithms for the 4 model sequences (A) A1, (B) N1, (C) R1, and (D) R2. Statistical 1$\sigma$ errors, estimated from 32 independent runs for each method (see Table~II), are shown but are smaller than the plot symbols for all points.}
\end{figure}

\end{document}
